Modelos

### 2019-01-21 20190117_modelos.Rmd
MONDAY01

# bjw <- 'just=~JW1+JW2+JW3+JW4+JW5'
bjw <- 'just=~JW2+JW3+JW4+JW5'

# fit <- cfa(model = bjw,data = st,ordered = c("JW1","JW2","JW3","JW4","JW5"))
fit <- cfa(model = bjw,data = st,ordered = c("JW2","JW3","JW4","JW5"))

>>>>

bjw <- 'just=~JW1+JW2+JW3+JW4+JW5'
bjw <- 'just=~JW2+JW3+JW4+JW5'

# fit <- cfa(model = bjw,data = st,ordered = c("JW1","JW2","JW3","JW4","JW5"))
fit <- cfa(model = bjw,data = st,ordered = c("JW1","JW2","JW3","JW4","JW5"))

fit <- cfa(model = bjw,data = st,ordered = c("JW2","JW3","JW4","JW5"))
